\section{Datasets}
\label{sec:meth}

%Data set (5 points): Is the data set completely ready (in-hand, loaded onto a machine, analyzed for outliers or other problems)? Have some main features of the data set been characterized (either visually or statistically)?

We are mainly interested in pattern recognition related datasets.
All the datasets are available online.
In order to conduct experiments, we need to load the datasets into our
model and fine-tune parameters of the model.
We have been primarily working on MNIST and CIFAR. We plan to
conduct experiment on three to four datasets in total if time permitted.

\subsection{MNIST}
MNIST is a data set of handwritten digits. It contains a training set of
60,000 examples and a test set of 10,000 examples. The digits have been
size-normalized and centered in a fixed-size image.

We used this data set in our first step experiments. (See Experimental
Results for more details.)

\subsection{CIFAR}
CIFAR-10 is a data set of 60000 32x32 colour images in 10 classes, with 6000 images per class. There are 50000 training images and 10000 test
images.
CIFAR-100 is just like CIFAR-10, expect that it has 100 classes containing
600 images each. There are 500 training images and 100 testing images per
class.

We have succesfully loaded this dataset, and we are working on
fine-tuning parameters of the model to better fit this dataset.

\subsection{Other data sets}
Besides the above datasets, we plan to conduct experiements on
datasets such as Street View House Numbers (SVHN) and NORB as well.

