\documentclass{article} % For LaTeX2e
\usepackage{nips14submit_e,times}
\usepackage{hyperref}
\usepackage{url}
%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09


\title{Deep Learning With Noise}

\author{
Yixin Luo \\
Computer Science Department \\
Carnegie Mellon University \\
\texttt{yixinluo@cs.cmu.edu} \\
\And
Fan Yang\\
Department of Mathematicsl Sciences \\
Carnegie Mellon University \\
\texttt{fanyang1@andrew.cmu.edu} \\
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\nipsfinalcopy % Uncomment for camera-ready version

\begin{document}

\maketitle

\begin{abstract}

\end{abstract}

\section{Question and Goals}
Question and Goals (10 points): State the updated version of the research question, based on results so far. Is it well-formed and interesting? Are there well-defined metrics for success? Is the minimum goal achievable in the remaining time? Are the stretch goals interesting?

\section{Data set}
Data set (5 points): Is the data set completely ready (in-hand, loaded onto a machine, analyzed for outliers or other problems)? Have some main features of the data set been characterized (either visually or statistically)?

\section{First Steps and Evaluation}
First Steps and Evaluation (10 points): Were the first steps described in the project proposal completed? Are there nontrivial preliminary results in terms of system performance or data collection (if data collection is a significant part of the project)? Is the interpretation of these results careful and correct? Is there an assessment of where the project stands? Are next steps clear, including any course corrections based on preliminary results?

\end{document}
